Draft final report\\ Measles risk assessment, modelling and benefit--cost analysis\\ \vspace{2 mm} {\large David T S Hayman, Tim Carpenter,\\ Jonathan C Marshall, Mick Roberts, Nigel P French}

### 2014-10-28 draftfinalreport.Rnw
Inserted figures

%%%%%%%%%%%%%%%%%%%
% INSERT NZ Travelers here
%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%
% INSERT Total Travelers here
%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[h!]
\begin{center}
<<fig=TRUE,echo=FALSE,width = 11>>=
print(np1)
@
\end{center}
\caption{Immigration to New Zealand 2012}
\label{fig:immigration12}
\end{figure}

%%%%%%%%%%%%%%%%%%%
% INSERT NZ Travellers here
%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%
% INSERT Total Travelers here
%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[h!]
\begin{center}
<<fig=TRUE,echo=FALSE,width = 11>>=
print(np4)
@
\end{center}
\caption{Risk map from measles incidence and immigration rates}
\label{fig:risk12}
\end{figure}

%%%%%%%%%%%%%%%%%%%
% INSERT Total risk here
%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%% ADD NAIVE ## BY DHB HERE

%%%%%%%%%%%%%%%%%%%
% ADD REPORT # 2 RISK ANAYSIS HERE
%%%%%%%%%%%%%%%%%%
\subsection{Regression analyses results}
\label{sub:regression_results}

>>>>

%%%%%%%%%%%%%%%%%%%%%
% INSERT NZ Travlers here
%%%%%%%%%%%%%%%%%%%
% INSERT Total Travelers here
%%%%%%%%%%%%%%%%%%

@@

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{np1.pdf}
     \caption{Non-New Zealander travel}
     \label{fig:immigration12}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{nznp1.pdf}
     \caption{New Zealand travellers 2012}
     \label{fig:nztravellers}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{totnp1.pdf}
     \caption{Total travellers 2012}
     \label{fig:tottravellers}
\end{figure}

@@

\begin{figure}[h!]
 \centering
 \includegraphics[width=0.8\textwidth]{np4.pdf}
\caption{Risk map from measles incidence and immigration rates}
\label{fig:risk12}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{nznp4.pdf}
     \caption{Risk map from measles incidence and New Zealander travel rates}
     \label{fig:nzrisk12}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{totnp4.pdf}
     \caption{Risk map from measles incidence and total travel rates}
     \label{fig:totrisk12}
\end{figure}

@@

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{naive_map.pdf}
     \caption{Numbers of naive individuals per District Health Board}
     \label{fig:naive_map}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb1.pdf}
     \caption{Numbers of naive individuals per age class, Northland District Health Board}
     \label{fig:Northland}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb2.pdf}
     \caption{Numbers of naive individuals per age class, Waitemata District Health Board}
     \label{fig:Waitemata}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb3.pdf}
     \caption{Numbers of naive individuals per age class, Auckland District Health Board}
     \label{fig:Auckland}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb4.pdf}
     \caption{Numbers of naive individuals per age class, Counties Manukau District Health Board}
     \label{fig:Counties_Manukau}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb5.pdf}
     \caption{Numbers of naive individuals per age class, Waikato District Health Board}
     \label{fig:Waikato}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb6.pdf}
     \caption{Numbers of naive individuals per age class, Lakes District Health Board}
     \label{fig:Lakes}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb7.pdf}
     \caption{Numbers of naive individuals per age class, Bay of Plenty District Health Board}
     \label{fig:BayofPlenty}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb8.pdf}
     \caption{Numbers of naive individuals per age class, Tairawhiti District Health Board}
     \label{fig:Tairawhiti}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb9.pdf}
     \caption{Numbers of naive individuals per age class, Taranaki District Health Board}
     \label{fig:Taranaki}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb10.pdf}
     \caption{Numbers of naive individuals per age class, Hawke's Bay District Health Board}
     \label{fig:HawkesBay}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb11.pdf}
     \caption{Numbers of naive individuals per age class, Whanganui District Health Board}
     \label{fig:Whanganui}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb12.pdf}
     \caption{Numbers of naive individuals per age class, Midcentral District Health Board}
     \label{fig:Midcentral}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb13.pdf}
     \caption{Numbers of naive individuals per age class, Hutt District Health Board}
     \label{fig:Hutt}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb14.pdf}
     \caption{Numbers of naive individuals per age class, Capital and Coast District Health Board}
     \label{fig:CapitalandCoast}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb15.pdf}
     \caption{Numbers of naive individuals per age class, Wairarapa District Health Board}
     \label{fig:Wairarapa}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb16.pdf}
     \caption{Numbers of naive individuals per age class, Nelson Marlborough District Health Board}
     \label{fig:NelsonMarlborough}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb16.pdf}
     \caption{Numbers of naive individuals per age class, West Coast District Health Board}
     \label{fig:WestCoast}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb17.pdf}
     \caption{Numbers of naive individuals per age class, Canterbury District Health Board}
     \label{fig:Canterbury}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb18.pdf}
     \caption{Numbers of naive individuals per age class, South Canterbury District Health Board}
     \label{fig:SouthCanterbury}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{dhb19.pdf}
     \caption{Numbers of naive individuals per age class, Southern District Health Board}
     \label{fig:Southern}
\end{figure}

\subsection{Regression analyses results}
\label{sub:regression_results}
